Computer Science House Constitution

### 2018-02-06 articles.tex
Fixed some spelling mistakes

% ARTICLE VII - TEMPORARY AMENDMENTS
\article{Temporary Amendments}
In the case that an amendment should be temporary, the amendment's changes should be listed here. 
Each of these amendments is given a designated period of time, and will cease to exist immedietely. 
If at any point interpretation of the changes needs to be made, the Executive Board will use the process defined in \ref{Judicial} to come to an agreement on how to proceed. 
Occasionaly, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
\asection{Changes to Evaluations}
During the 2018-2019 period the following will supercede the text otherwise found in this document.
\asubsection{Changes}
\asubsubsection{Removal of Introductory Project}
\ref{The Introductory Project} will no longer be a requirement as described in \ref{The Introductory Process}. 
Additionally, \ref{Introductory Executive Board} will also no longer be elected or perform any duties during the described period. 
\asubsubsection{Change of Packet Percentage}
\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations. 
During the described period, the percentage of required signatures in the Introductory Packet is increased to 75\%. 
\asubsubsection{Changes to Packet Distribution}
Introductory Members will recieve an \ref{The Introductory Packet} at the begining of the second week of each semester. 
Any applicants who wish to become Introductory Members after the third week of each semester will recieve their packet during the begining of the second week of the following semester. 
During the first, second, or third week of each semester, any applicant may have their application evaluated during a standard Evaluations Directorship Meeting or during either House Meeting or an Executive Board Meeting. 
\asubsubsection{PR Director} 
Public Relations Director is added to \ref{Voting Members}, and is given the following responsibilities during the described period.  
\begin{enumerate}
	\item To preside over Public Relations Directorship Meetings.
	\item To exercise general supervision over the Public Relations operations.
	\item To communicate clearly with the Rochester Institute of Technology's extended community.
	\item To collaborate with the Social and Evaluations Directors to ensure that \ref{The Introductory Process} is directed correctly.
	\item To advertise any events run by Evaluations Director and/or Social Director(s) that are intended to be attended by RIT Students whom are not Computer Science House Members.  
\end{enumerate}
\asubsubsection{Evaluations and Social Directorship Changes}
The Evalutations Director and Social Director(s) will have the following additional responsibilities during the described period. 
\begin{enumerate}
	\item To preside over a number of events intended to produce interest in CSH, especially in RIT students during the begining weeks of each semester.
\end{enumerate}
\asubsubsection{Evaluation Period}
During the described period, the \ref{The Introductory Process} will begin during the first week of each semester or when the Evaluations Director otherwise chooses to initiates it.
The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period. 
\subsubsection{Referendum}
During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
\end{document}

>>>>

% ARTICLE VII - TEMPORARY AMENDMENTS
\article{Temporary Amendments}
In the case that an amendment should be temporary, the amendment's changes should be listed here. 
Each of these amendments is given a designated period of time, and will cease to exist immediately.
If at any point interpretation of the changes needs to be made, the Executive Board will use the process defined in \ref{Judicial} to come to an agreement on how to proceed. 
Occasionaly, Temporary Amendments may become permanent through a referendum, which is described in detail as part of each Temporary Amendment. 
\asection{Changes to Evaluations}
During the 2018-2019 period the following will supercede the text otherwise found in this document.
\asubsection{Changes}
\asubsubsection{Removal of Introductory Project}
\ref{The Introductory Project} will no longer be a requirement as described in \ref{The Introductory Process}. 
Additionally, \ref{Introductory Executive Board} will also no longer be elected or perform any duties during the described period. 
\asubsubsection{Change of Packet Percentage}
\ref{Creation of Accounts} currently stipulates that Introductory Members must acquire 60\% (rounded up to the nearest whole person) of required signatures (excluding those of Resident members who have not passed a Membership Evaluation) in the Introductory Packet or successfully complete Introductory Evaluations. 
During the described period, the percentage of required signatures in the Introductory Packet is increased to 75\%. 
\asubsubsection{Changes to Packet Distribution}
Introductory Members will recieve an \ref{The Introductory Packet} at the begining of the second week of each semester. 
Any applicants who wish to become Introductory Members after the third week of each semester will recieve their packet during the begining of the second week of the following semester. 
During the first, second, or third week of each semester, any applicant may have their application evaluated during a standard Evaluations Directorship Meeting or during either House Meeting or an Executive Board Meeting. 
\asubsubsection{PR Director} 
Public Relations Director is added to \ref{Voting Members}, and is given the following responsibilities during the described period.  
\begin{enumerate}
	\item To preside over Public Relations Directorship Meetings.
	\item To exercise general supervision over the Public Relations operations.
	\item To communicate clearly with the Rochester Institute of Technology's extended community.
	\item To collaborate with the Social and Evaluations Directors to ensure that \ref{The Introductory Process} is directed correctly.
	\item To advertise any events run by Evaluations Director and/or Social Director(s) that are intended to be attended by RIT Students whom are not Computer Science House Members.  
\end{enumerate}
\asubsubsection{Evaluations and Social Directorship Changes}
The Evaluations Director and Social Director(s) will have the following additional responsibilities during the described period. 
\begin{enumerate}
	\item To preside over a number of events intended to produce interest in CSH, especially in RIT students during the begining weeks of each semester.
\end{enumerate}
\asubsubsection{Evaluation Period}
During the described period, the \ref{The Introductory Process} will begin during the first week of each semester or when the Evaluations Director otherwise chooses to initiates it.
The Executive Board may hold a Simple Majority vote to extend the Introductory Process or the Introductory Packet during the described period. 
\subsubsection{Referendum}
During the last house meeting of the second semester of the described period, a Two-Thirds vote is held, and if it passes, \ref{Changes to Evaluations} becomes permanent. 
\end{document}
